CPU-Scheduling

### 2024-10-20 Handout/article.tex
created main.py and stuff

\subsubsection{Introduction}
Here we'll look at policies doesn't "just invent".
These are usually more sophisticated and can be hypothetically used in a real system (at least with some adjustemts). 
First we'll look at the Multi-Level Feedback Queue, short MLFQ. 
This is one of the most known ones an is used in Solaris.
The creator Fernando J. Corbató even recieved a Turing Award for it in 1990.
First I'll write down some abstract rules. These are usually complemented with an example. 
After that there will be a quick implementation of the policy in C++.
Please feel free to jump around to get a better grasp of the (theory).

@@

\noindent So as "OSTEP REFERENCE HERE" would summarize it:
\begin{enumerate}
  \item If Priority (A) $>$ Priority (B) $\Rightarrow$ A runs \& B doesn't
  \item If Priority (A) = Priority (B) $\Rightarrow$ A \& B run in RR
  \item When a job enters the system, it is placed at the highest priority
  \item Once a job uses up its time allotment at a given level, its priority is reduced
  \item After some period S, move all the jobs in the system to the topmost queue
\end{enumerate}

@@

>>>>

\subsubsection{Introduction}
Here we'll look at policies doesn't "just invent".
These are usually more sophisticated and can be hypothetically used in a real system (at least with some adjustemts). 
First we'll look at the Multi-Level Feedback Queue, short MLFQ. 
This is one of the most known ones an is used in Solaris.
The creator Fernando J. Corbató even recieved a Turing Award for it in 1990.
First I'll write down some abstract rules. These are usually complemented with an example. 
After that there will be a quick implementation of the policy in Python.
Please feel free to jump around to get a better grasp of the (theory).

@@

\noindent So as "OSTEP REFERENCE HERE" would summarize it: DO I EVEN NEED THIS?
\begin{enumerate}
  \item If Priority (A) $>$ Priority (B) $\Rightarrow$ A runs \& B doesn't
  \item If Priority (A) = Priority (B) $\Rightarrow$ A \& B run in RR
  \item When a job enters the system, it is placed at the highest priority
  \item Once a job uses up its time allotment at a given level, its priority is reduced
  \item After some period S, move all the jobs in the system to the topmost queue
\end{enumerate}

@@

For the whole script, please checkout my Github. There you can find

\begin{lstlisting}[language=Python, style=colorEX]
    # Implementation of MLFQ in Python
